---
title: "Case study"
author: "Akhil"
date: "2023-02-12"
output:
  html_document: default
  word_document: default
---
---
title: "Akhil case study"
output: html_document
---

## Bella beat
Bellabeat is a successful small company, but they have the potential to become a larger player in the global smart device market.


## FitBit Fitness Tracker Data
CC0: Public Domain, dataset made available through Mobius:
https://www.kaggle.com/arashnic/fitbit


## Loading packages and libraries

```{r loading pack}
library(tidyverse)
library(ggplot2)
```


## Loading files

```{r}
daily_activity <- read.csv("dailyActivity_merged.csv")
```

We'll create another dataframe for the sleep data. 
```{r}
sleep_day <- read.csv("sleepDay_merged.csv")
```

## Exploring a few key tables

Take a look at the daily_activity data.
```{r}
head(daily_activity)
```

Identify all the columsn in the daily_activity data.
```{r}
colnames(daily_activity)
```

Take a look at the sleep_day data.
```{r}
head(sleep_day)
```

Identify all the columsn in the daily_activity data.
```{r}
colnames(sleep_day)
```

That both datasets have the 'Id' field - this can be used to merge the datasets.

## Understanding some summary statistics
How many unique participants are there in each dataframe? It looks like there may be more participants in the daily activity dataset than the sleep dataset.

```{r distinct users}
n_distinct(daily_activity$Id)
n_distinct(sleep_day$Id)
```

How many observations are there in each dataframe?
```{r observations}
nrow(daily_activity)
nrow(sleep_day)
```

What are some quick summary statistics we'd want to know about each data frame?

For the daily activity dataframe:
```{r}
daily_activity %>%  
  select(TotalSteps,
         TotalDistance,
         SedentaryMinutes) %>%
  summary()
```

For the sleep dataframe:
```{r}
sleep_day %>%  
  select(TotalSleepRecords,
  TotalMinutesAsleep,
  TotalTimeInBed) %>%
  summary()
```



## visualization

Relationship between steps taken in a day and sedentary minutes

```{r}
ggplot(data=daily_activity, aes(x=TotalSteps, y=SedentaryMinutes)) + geom_point()
```

The relationship between minutes asleep and time in bed

```{r}
ggplot(data=sleep_day, aes(x=TotalMinutesAsleep, y=TotalTimeInBed)) + geom_point()
```

What could these trends tell you about how to help market this product? Or areas where you might want to explore further?

## Merging these two datasets together

```{r}
combined_data <- merge(sleep_day, daily_activity, by="Id")
```

Take a look at how many participants are in this data set.

```{r}
n_distinct(combined_data$Id)
```
Thank you for attention!


